Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 algorithm.tex
edits in problem definition, carried through to proofs

We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.

@@

We begin by showing that under our assumptions, the measure of
problematic arms cannot be too large.

\begin{lemma} \label{lem:sdelta}
$\AlmostTied{\delta} \leq \TieDensity \cdot \delta$ for all $\delta$.
\end{lemma}

\begin{emptyproof}
Using the upper bound from Assumption~\ref{A1}, we can bound

\begin{align*}
\AlmostTied{\delta}
& = \sum_{i,i'} \ProbC{\AgV \cdot (\ArmV{i} - \ArmV{i'}) \leq \delta}%
    {\AgV \in \FirstTwo{i}{i'}}
  \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}\\
& \leq \sum_{i,i'} \TieDensity \cdot \delta
    \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}
\; = \; \TieDensity \cdot \delta. \QED
\end{align*}
\end{emptyproof}

We next bound the length of any phase, which will be useful to bound
the cumulative regret of the early rounds
(before tail bounds have kicked in).

@@

By Lemma~\ref{lem:sdelta}, the measure of agents (across all arms)
whose best and second-best arm differ in utility by less
than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
In particular, this bound holds for agents whose best arm is $i$.
By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
will myopically pull arm $i$.
Because $1/\log(s) < \frac{\MinProb}{2}$ for
$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
$\tau_s$.
\end{proof}

@@

We first consider agents \AgV incurring positive regret less than $g(s)$.
The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
By Lemma~\ref{lem:sdelta}, the total measure of such agents
is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
and each incurs regret at most $g(s)$.
Summing over all time steps,
and using Lemma~\ref{lem:phase-length} to bound the number of time
steps in phase $s$, 
the expected total regret from such agents is at most
\begin{align}
\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)}
& \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
\label{equ:small_regret_bound}
\end{align}

>>>>

%We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.

@@

% We begin by showing that under our assumptions, the measure of
% problematic arms cannot be too large.

% \begin{lemma} \label{lem:sdelta}
% $\AlmostTied{\delta} \leq \TieDensity \cdot \delta$ for all $\delta$.
% \end{lemma}

% \begin{emptyproof}
% Using the upper bound from Assumption~\ref{A1}, we can bound

% \begin{align*}
% \AlmostTied{\delta}
% & = \sum_{i,i'} \ProbC{\AgV \cdot (\ArmV{i} - \ArmV{i'}) \leq \delta}%
%     {\AgV \in \FirstTwo{i}{i'}}
%   \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}\\
% & \leq \sum_{i,i'} \TieDensity \cdot \delta
%     \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}
% \; = \; \TieDensity \cdot \delta. \QED
% \end{align*}
% \end{emptyproof}

We begin by bounding the length of any phase, which will be useful to bound
the cumulative regret of the early rounds
(before tail bounds have kicked in).

@@

By Assmption~\ref{A1},
%Lemma~\ref{lem:sdelta},
the measure of agents (across all arms)
whose best and second-best arm differ in utility by less
than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
In particular, this bound holds for agents whose best arm is $i$.
By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
will myopically pull arm $i$.
Because $1/\log(s) < \frac{\MinProb}{2}$ for
$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
$\tau_s$.
\end{proof}

@@

We first consider agents \AgV incurring positive regret less than $g(s)$.
The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
By Assumption~\ref{A1},
%Lemma~\ref{lem:sdelta},
the total measure of such agents
is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
and each incurs regret at most $g(s)$.
Summing over all time steps,
and using Lemma~\ref{lem:phase-length} to bound the number of time
steps in phase $s$, 
the expected total regret from such agents is at most
\begin{align}
\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)}
& \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
\label{equ:small_regret_bound}
\end{align}
